---
title: "rat-strain-test"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
library(readxl)
library(janitor)
```

## Big question - can we differentiate acute from chronic.
These are coded (acute = week 1, chronic = week 6)

which match categories 2 and 4 in Laura sent data table

## Reading in Data

We will start with a single file of the 42? files
all located at Dropbox
/US_nonlinearRO1_2015/RTNSBS30-shear strain map/

```{r read}
backwall_32_4 <-readxl::read_xlsx("EI_Backwall2RTNBS32-4shearcorrected_Res_UNKNOWN_UNKNOWN_PlotData_1-159.xlsx") %>% 
  clean_names
```

This contains 159 rows, delineated by time (0-10 seconds), for one rat. This represents one push, with 6 ROIs for this particular rat.


Select a manageable set of columns
```{r}
select <- backwall_32_4 %>% 
  select(time_seconds, contains("shear_strain_along_axis")) 
```
total of 85 col
Get 
- time_seconds
- shear_strain_along_axis (6)
- shear_strain_along_axis_hd_segment_roi (1-18)(1-18)
- shear_strain_across_axis (6)
- shear_strain_across_axis_hd_segment_roi (1-18)(1-18)

```{r}
select %>% 
  select(time_seconds, contains("along") & !contains("roi")) %>% 
  pivot_longer(
    cols = contains("along"),
    names_to = "seg",
    names_prefix = "shear_strain_along_axis_hd_segment_",
    values_to = "ss_along_ax",
    values_drop_na = TRUE
  ) %>% 
  filter(seg==6) %>% 
  mutate(slope = min(ss_along_ax) - max(ss_along_ax)/(max(time_seconds) - min(time_seconds)))
```

- should we include sub-roi data?
- how do we collapse across ROIs? throw out some?
- how do we collapse across time points? slope?
acceleration? remove zero time? remove points where it is unchanging?

- possibly slope by segment, then throw out segments with outlying slope? or take median slope? Exclude early and late times (when flattens out)
